CODECHECK: An open-science initiative for the independent execution of computations underlying research articles

### 2021-01-12 codecheck-paper.tex
update tools

The \texttt{codecheckers} GitHub organisation\footnote{
\url{https://github.com/codecheckers}} contains projects managing the
project website, the community of codecheckers, community discussions,
forks of codechecked code repositories, and the main register for
managing the collection of checks. Both the website\footnote{
\url{https://codecheck.org.uk/}} and the register
\footnote{\url{https://codecheck.org.uk/register}} are hosted as GitHub
pages. The register is effectively a single table in CSV format that
connects the certificate identifier with the repository associated with
a specific conducted codecheck. Each of these repositories, which 
currently can be hosted on GitHub or Open Science Framework (OSF), 
contains the CODECHECK metadata file \texttt{codecheck.yml}. The register
further contains a column for the type of check, e.g., community, journal,
or conference, and the respective GitHub issue where communications and 
assignments around a specific check are organised. No information is 
duplicated between the register and the metadata files. When a new
certificate is entered into the register, an automated process using 
continuous integration infrastructure of GitHub, GitHub Actions, retrieves
the metadata files and builds different representations of the register
for viewing (HTML) or integration with other services (CSV, JSON).

Zenodo is an open repository for scientific data and documents. It
mints DOIs for deposits and ensures long-term availability of all digital
artefacts related to the project. These include the community 
certificates as well as the register, which is regularly archived to 
Zenodo \cite{codecheck_register} (including all file formats).

A custom R package, \texttt{codecheck}\footnote{
\url{https://github.com/codecheckers/codecheck}}, helps with the authoring
of certificates, and with the deposition of certificates and reated files to
Zenodo using the R package \texttt{zen4R} \cite{zen4r}.
Codecheckers may choose to not use the package and rely on their own tools
for creating the certificate. This is a deliberate flexibility to
accomodate both different skill sets and unforseen technical advances or
challenges.

These tools and resources demonstrate that a CODECHECK process can be
managed without infrastructure costs on freely available platforms.
The scripted and automated parts should also ensure that more checks can
be conducted in the future, though the management by a paid CODECHECK
editor or further automation, e.g., with a bot, could improve turnaround time.
The remaining costs are the project's domain, which is negligible, and
the human resources for managing the project and processes, which are
considerable and currently solely based on, partly grant-based, public funding.
Naturally, similar set-ups are possible, such as using GitLab/GitLab.com 
and the GitLab CI instead of GitHub and GitHub Actions, or using a different 
data repository for depositing certificates and data.

>>>>

The \texttt{codecheckers} \textbf{GitHub} organisation\footnote{
\url{https://github.com/codecheckers}} contains projects for managing the
project website, the community of codecheckers, community discussions,
forks of checked code repositories, and the main register of 
CODECHECKs. Both the website\footnote{
\url{https://codecheck.org.uk/}} and the register\footnote{
\url{https://codecheck.org.uk/register}} are hosted as GitHub
pages. The register is a single table in CSV format that
connects the certificate identifier with the repository associated with
a specific conducted CODECHECK. Each of these repositories, which 
currently can be hosted on GitHub or Open Science Framework (OSF), 
contains the CODECHECK metadata file \texttt{codecheck.yml}. The register
further contains a column for the type of check, e.g.,~community, journal,
or conference, and the respective GitHub issue where communications and 
assignments around a specific check are organised. No information is 
duplicated between the register and the metadata files. When a new
certificate is entered into the register, an automated process using the
continuous integration infrastructure of GitHub, GitHub Actions, retrieves
all metadata files and builds different representations of the register
for viewing (HTML) and for integration with other services (CSV, JSON).

\textbf{Zenodo} is an open repository for scientific data and documents. It
mints DOIs for deposits and ensures long-term availability of all digital
artefacts related to the project. These include the community 
certificates as well as the regularly archived register \cite{codecheck_register}.

A \textbf{custom R package}, \texttt{codecheck}\footnote{
\url{https://github.com/codecheckers/codecheck}}, helps with the authoring
of certificates, and with the deposition of certificates and realed files to
Zenodo using the R package \texttt{zen4R} \cite{zen4r}.
Codecheckers may choose to not use the package and rely on their own tools
for creating the certificate, even a simple word processor.
This is a deliberate flexibility to
accomodate different skill sets and unforseen technical advances or
challenges.

These tools and resources demonstrate that a CODECHECK process can be
managed without infrastructure costs on freely available platforms.
The automation should ensure that more checks can
be conducted in the future, though the management by a paid CODECHECK
editor or further automation, e.g.,~with a bot, could improve turnaround time.
The only costs are the project's domain, which is negligible.
This leaves the initiative's main resource -- the \textbf{humans}
for managing the project and processes and the codecheckers.
All contributions are currently rely on (partly grant-based) public funding
and volunteering.
Naturally, similar set-ups are conceivable, such as using GitLab.com or
a hosted GitLab instance and the GitLab continuous integration.
